### 2016-08-19 ms/ms.tex
worked on discussion

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
The mostly widely explored mechanism of network assembly, preferential
attachment \citep{barabasi1999emergence}, predicts that a new species
is more likely to interact with species that are already
well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
mechanism of assembly. Investigating the day-to-day, temporal assembly
of a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, likely because these species are either more abundant or more
temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} found some indication
assembly was occurring through preferential attachment. Network
nestedness, a pattern of interactions where a generalist core
interacts with both specialist and generalist species, increased as
the community aged \citep{albrecht2010plant}. Increasing nestedness
could result from a process like preferential attachment where
specialist species attach to the well-connected, generalist core.

@@

% Even non-successional temporal dynamics suggest a stable core of
% generalists persist despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

@@

There were no consistent trends as to when change points occurred
within assembling hedgerows or across all sites, except many site had
changing points between year 2009 and 2011 (Fig.~
\ref{fig:changePoints}). In California, 2011 marked the beginning of a
multi year drought. In the assembling hedgerows were not sampled in
2010, so disentangling whether the changing points are due to skipping
a year of assembly or the drought is not impossible. Interestingly,
most of the assembling hedgerows

The species that were most variable in their network position and thus
contributed most to network reorganizations where species with the
highest degrees (i.e., most generalized) and persistence.  For
example, the five most ubiquitous species in our study landscape ---
\textit{Halictus ligatus}, \textit{Halictus
  tripartitus},\textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- where also the only species that
changed what module (i.e., community) they were present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentable
the causal mechanism for why species with their chatacterists are so
variable in their network position. Generalized species may be best
able to exploit the limited floral resources the intensivly managed
agriculture landscape, and thus also most persistent. These adaptable
species will take advanatge of the most advantage resrouces, which my
depend the other pollinator species that are present and the state of
the floral resource. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a high degree.  Either way, our results suggest
that highly persisitent and generalized species often change their
network positions.

Preferential attachment is the most widely accepted theory explaining
community assembly in mutualistic networks. Communities assembling
through preferential attachment are formed by a core of generalist
species, to which new species arriving to the community interact
with. Thus, communities assembling through preferential attachment
exhibit an increase both in nestedness and in the overall level of
species specialization, since specialist species are being added to
the community. However, our changing point analysis results show that
there is a critical reorganization in the interaction patterns as
communities assembly, which contradicts the preferential attachment
theory. Even though we encountered an increase in nestedness through
time, specialization did not increase. Furthermore, this increase in
nestedness could be explained by the increase in species
richness. blablabla mechanistic models.

%% not sure if we want to go here, since it is not really part of the
%% assembly story. More just a "hmm networks are structured in odd
%% ways sometimes"  
% Other interesting result is that even though nestedness increased
% through time, modularity and connectance did not. \cite{Fortuna2010}
% suggest that at low connectance levels, mutualistic networks would
% present high nestedness and high modularity, while at high connectance
% levels networks would present low nestedness and low
% modularity. However, our results show the contrary: early communities
% presented low nestedness, smaller richness, and higher levels of
% modularity and connectance, while more mature communities presented
% higher nestedness, higher richness, and smaller modularity and
% connectance. SO blabla... XX Temporal overlap.

High nestedness has been related to an increase in the robustness of
communities to species extinctions because the core of generalist
species would act as a buffer against species loss (REF). Similarly,
communities with greater modularity would be more robust in general,
because modules would act as a buffer against perturbation spreading
and the pervasive effects of species loss. We expected that as
communities assemble and species richness increase, communities would
become increasingly robust to species loss. however, we found that
robustness to species loss did not change through time. This is
interestingly from the conservation biology point of view, because
even early assembling communities seem to be as robust as more mature
communities, despite the richness insurance hypothesis. However,
communities are not only subjected to species loss, but also to other
types of perturbations that can cascade through the network. Gaiarsa
et al. (submitted) suggest using algebraic connectivity to explore
how vulnerable ecoogical communities might be to cascading
effects. Our results indicate that more mature communities are more
robust to cascading effects than early on assemblages, and that this
result is related to species richness. This migth be related to XX....

@@

>>>>

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
The mostly widely explored mechanism of network assembly, preferential
attachment \citep{barabasi1999emergence}, predicts that a new species
is more likely to interact with species that are already
well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
mechanism of assembly. Investigating the day-to-day, temporal assembly
of a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, likely because these species are either more abundant or more
temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} found some indication
assembly was occurring through preferential attachment. Network
nestedness, a pattern of interactions where a generalist core
interacts with both specialist and generalist species, increased as
the community aged \citep{albrecht2010plant}. Increasing nestedness
could result from a process like preferential attachment where
specialist species attach to the well-connected, generalist core.  In
addition, non-successional temporal dynamics also suggest a stable
core of generalists persists despite high turnover of peripheral
species \citep{fang2012relative, diaz2010changes, alarcon2008year}.

@@

@@

There were no consistent trends in when change points occurred within
assembling hedgerows or across all sites, except many sites had
changing points between year 2009 and 2011 (Fig.~
\ref{fig:changePoints}). In California, 2011 marked the beginning of a
multi-year drought. In the assembling hedgerows were not sampled in
2010, so disentangling whether the changing points are due to skipping
a year of assembly or the drought is not impossible. Interestingly,
most of the assembling hedgerows did not undergo a signficiant
reorganization of interactions immediatly the hedgerow was planted
(i.e., the transition from weedy field margin to hedgerow). This
result is consistent with other studies finding that the gains in
species richness of both the plant and pollinators takes several years
post-restoration (Kremen and M'Gonigle, in prep).

Surprisingly, the species that were most variable in their network
position and thus contributed most to network reorganizations where
species with the highest degrees (i.e., most generalized) and
persistence.  For example, the five most ubiquitous species in our
study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus},\textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- where also the only species that
changed what module (i.e., community) they were present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentable
the causal mechanism for why species with their chatacterists are so
variable in their network position. Generalized species may be best
able to exploit the limited floral resources the intensivly managed
agriculture landscape, and thus also most persistent. These adaptable
species will take advanatge of the most advantage resources, which my
depend the other pollinator species that are present and the state of
the floral resource. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a high degree. Either way, our results suggest
that given the opportunity and ability to use different resources,
species will often their network positions.

%% node/species turnover

The frequent changing points in network organization, dynamic nature
of the location of species in networks, and turnover of species and
nodes all point to an assembly mechanism other than preferential
attachment. Nestedness did increase with years post restoration, as
would be expected if colonizing, specialist species attached to a
central, generalist core. With preferential attachment, however, we
could also expect connectance and specialization to increase, and see
neither. The increase in nestedness is thus more likely a consequence
of the enhancement of species richness through time \flagged{DO WE
  HAVE CITATIONS FOR THIS?}. In addition, though the colonization and
persistence of floral specialists increases with assembly
\citep{mgonigle-2015-x}, this must be accumpanied changes in the diet
breat of the present species in order for network-level specialization
to remain constant through time.

Preferential attachment is the most widely accepted theory explaining
network assembly, but few ecological studies have been conducted that
test for this mechanism \citep{Olesen2008}. \flagged{other
  citations??}. Though \cite{Olesen2008} found some evidence for an
assmbly process like prefrential attachment governming the temporal
build up of plant-pollinator networks within a season, the frequent
reorganizations of the hedgerow communities suggest a very different
mechanism is at play. Plant-pollinator networks in general are highly
dynamic, with high turnover of species and interactions both within
and between seasons \citep{Burkle2011}. Though our non-assembling
communities experience fewer network reorganizations than the
assembling hedgerows, $82\%$ of field marings and $40\%$ of mature
hedgerows underwent at least one changing point in network
structure. Few alternative models to perferential attachment that
predict these network reorganizations have been explored, however.

Complementarity between traits like tounge length and corolla depth as
well as body and flower impose some biophysical limits to the
interactions between plants and pollintors
\citep{Vazquez2009evaluating, Stang2009, Stang2006,
  Santamaria2007}. Similarly, the phenologies of plants and
pollinators must also overlap \citep{Vazquez2009,
  Vazquez2009evaluating}.

 \citep{valdovinos2013adaptive}

The changes in network patterns with assembly also increased the
robustness of the networks to perturbation, but not to plant species
loss.

The increase in nestedness has been related to an increase in the
robustness of communities to species extinctions because the core of
generalist species would act as a buffer against species loss
(REF). Similarly, communities with greater modularity would be more
robust in general, because modules would act as a buffer against
perturbation spreading and the pervasive effects of species loss. We
expected that as communities assemble and species richness increase,
communities would become increasingly robust to species loss. however,
we found that robustness to species loss did not change through
time. This is interestingly from the conservation biology point of
view, because even early assembling communities seem to be as robust
as more mature communities, despite the richness insurance
hypothesis. However, communities are not only subjected to species
loss, but also to other types of perturbations that can cascade
through the network. Gaiarsa et al. (submitted) suggest using
algebraic connectivity to explore how vulnerable ecoogical communities
might be to cascading effects. Our results indicate that more mature
communities are more robust to cascading effects than early on
assemblages, and that this result is related to species richness. This
migth be related to XX....

%% not sure if we want to go here, since it is not really part of the
%% assembly story. More just a "hmm networks are structured in odd
%% ways sometimes" and we dont' really have answer for why this is
%% happening...

% Other interesting result is that even though nestedness increased
% through time, modularity and connectance did not. \cite{Fortuna2010}
% suggest that at low connectance levels, mutualistic networks would
% present high nestedness and high modularity, while at high connectance
% levels networks would present low nestedness and low
% modularity. However, our results show the contrary: early communities
% presented low nestedness, smaller richness, and higher levels of
% modularity and connectance, while more mature communities presented
% higher nestedness, higher richness, and smaller modularity and
% connectance. SO blabla... XX Temporal overlap.

@@

% Communities assembling through preferential attachment are formed by a
% core of generalist species, to which new species arriving to the
% community interact with. Thus, communities assembling through
% preferential attachment exhibit an increase both in nestedness and in
% the overall level of species specialization, since specialist species
% are being added to the community. However, our changing point analysis
% results show that there is a critical reorganization in the
% interaction patterns as communities assembly, which contradicts the
% preferential attachment theory. Even though we encountered an increase
% in nestedness through time, specialization did not
% increase. Furthermore, this increase in nestedness could be explained
% by the increase in species richness. blablabla mechanistic models.
